Learning \wat \sergey{here should be learning and not discovering, right?} constraints in spreadsheets and tabular data

### 2016-09-08 Paper/ECAI/tabular.tex
uncommitted tweaks

First, it borrows techniques from logical and relational learning \cite{luc_book}, as it finds
constraints in multiple relations (or tables). However, unlike typical logical and relational learning
approaches, it focuses on data in spreadsheets and constraints on columns or rows in the sheets.
Furthermore, it derives a set of simple ``atomic'' constraints rather than a set of rules that each consist of multiple literals as in clausal discovery \cite{claudien,lallouet}. Nevertheless, several ideas from logical and relational learning
proved to be useful, such as the use of a canonical form, a refinement graph, and pruning for redundancy. \sergey{that's where I added a new reference, needs to be checked and might need to be moved in the right place}. It also connects with the logical generalization of given formulas in a spreadsheet \cite{Isakowitz}, where one abstracts present formulas by introducing parameters in the place of particular cell references. The key difference here that we start not from existing formulas but from the data directly.

>>>>

First, it borrows techniques from logical and relational learning \cite{luc_book}, as it finds
constraints in multiple relations (or tables). Unlike typical logical and relational learning
approaches, it focuses on data in spreadsheets and constraints on columns or rows in the sheets.
Furthermore, it derives a set of simple ``atomic'' constraints rather than a set of rules that each consist of a conjunction of literals as in clausal discovery \cite{claudien,lallouet}. Nevertheless, several ideas from logical and relational learning
proved to be useful, such as the use of a canonical form, a refinement graph, and pruning for redundancy. \sergey{that's where I added a new reference, needs to be checked and might need to be moved in the right place}. It also connects with the logical generalization of given formulas in a spreadsheet \cite{Isakowitz}, where one abstracts present formulas by introducing parameters in the place of particular cell references. The key difference here that we start not from existing formulas but from the data directly.
